BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2014-01-19 tex/1-intro.tex
Add open-source to distinguish with the cited BF paper

\comment{NK: the article cited for the BlogForever platform already presents the proprietary web crawler used in the BlogForever project. To avoid confusion maybe we should slightly rephrase this sentence to: "This paper presents the open-source version of the BlogForever Crawler..." or similar?}
This paper presents the BlogForever Crawler, a key component of the BlogForever platform \cite{kasioumis2013towards} responsible for traversing blogs, extracting their content and monitoring their updates. Our main objective in this work is to design a crawler capable of extracting blog articles, authors, publication dates and comments. Our contributions can be summarized as follows:

>>>>

This paper presents the open-source BlogForever Crawler, a key component of the BlogForever platform \cite{kasioumis2013towards} responsible for traversing blogs, extracting their content and monitoring their updates. Our main objective in this work is to design a crawler capable of extracting blog articles, authors, publication dates and comments. Our contributions can be summarized as follows:
